My Findings

### 2024-03-20 Findings (Shared Folder)/Chapters/MolecularBiology.tex
new notes added

>>>>

\section{Some Histology}

In short, histology is the study of the animal tissue in the microscopic scale (which is also known as the microscopic anatomy or micro anatomy). Studying different types of animal tissue falls in the realm of histology.

\noindent There are four types of animal tissue 
\begin{enumerate}[(i),noitemsep]
	\item Epithelium
	\begin{itemize}
		\item squamous: endothelial lining of the vascular structure is of this type.
		\item cuboidal
		\item columnar
	\end{itemize}
	\item Muscle tissue
	\begin{itemize}
		\item smooth muscle
		\item skeletal muscle
		\item cardiac muscle
	\end{itemize}
	\item Connective tissue
	\begin{itemize}
		\item cartilage
		\item bone
		\item blood
		\item lymph
		\item hemopoietic
	\end{itemize}
	\item Nervous tissue
	\begin{itemize}
		\item central nervous system
		\item peripheral nervous system
	\end{itemize}
\end{enumerate}

Among this list of the four basic types of the animal tissue, we will focus on the Epithelium.

\subsection{Epithelium}
Epithelium forms continuous sheets of cells that line internal surfaces and cover the external surfaces of the organs. A \textbf{basement membrane} separates an epithelium from the underlying connective tissue.

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{images/histologySquamousEpithelial}
	\captionsetup{width=0.9\textwidth} 
	\caption{A) A microscopic image of renal corpuscle that contains a glomerulus (a tuft of capillaries) surrounded by Bowman's capsule. The interior of the capsule, is lined with a simple squamous epithelial that rests on a thick basement membrane. The only part of these cell visible is their nuclei bulging into the interior. B) Scanning electron microscope of renal corpuscle that its glomerulus is removed. The simple squamous epithelial can be seen in blue (borders of individual cells are not visible). Both images are from histologyguide.com.   }
	\label{fig:histologysquamousepithelial}
\end{figure}
\FloatBarrier

\begin{figure}[h!]
	\centering
	\includegraphics[width=0.8\linewidth]{images/bileDuct-SquamousEpithelialCells.png}
	\captionsetup{width=0.9\textwidth} 
	\caption{A pathology image of bile duct (the large lumen at the center). There are many blood vessels in the surrounding connective tissue. Blood vessels are lined with simple squamous epithelial. The only par of these cells visible is their flatten nuclei. \textbf{Epithelium that lines blood vessels, heart, and lymphatic vessels is also known as endothelium.}}

\end{figure}
